\section*{Abstract}
Secure multi-party computation (MPC) protocols often use correlated randomness to improve efficiency, allowing the scheme to be split into a computationally intensive offline preprocessing phase followed by a highly efficient input-dependent online phase. This approach is appealing because parties can now use previously unused idle time for preprocessing to speed up the time-critical part of their computation. Some schemes go further by realizing a non-interactive online phase, making them very attractive for high-latency environments, such as when participants are geographically dispersed. \textit{Pseudorandom correlation generators} (PCGs), as initiated by Boyle et al. (Crypto 2019, Crypto 2020), facilitate the preprocessing approach by allowing the generation of short correlated seeds that expand into long instances of a target correlation. PCGs offer sublinear communication complexity for seed generation and local expansion, reducing the communication required in the preprocessing phase. Despite the theoretical value of the primitive and its use in various MPC protocols in recent years, implementations of PCGs have been lacking.

This work addresses this gap by recalling the PCG construction proposed by Boyle et al., analyzing its building blocks, deriving practical considerations, and finally presenting an efficient implementation. Existing MPC protocols that use the PCG primitive for OLE and Vector-OLE correlations can use our implementation as a blueprint to efficiently implement their offline phase. We demonstrate the value of our practical considerations by implementing a PCG that realizes the offline phase of a non-interactive threshold BBS+ signature scheme by Faust et al. The PCG is the first for a threshold signature scheme to support the $t$-out-of-$n$ setting. It provides a quasilinear runtime for the number of presignatures generated, with a linear increase in runtime as participants are added. We provide benchmarks for up to $10$ parties and find that in the $2$-out-of-$2$ setting, our PCG generates $2^{17}$ presignatures in $100$ms per presignature while adding about $80$ms per additional party. This significantly outperforms (6x to 10x) the only other available PCG implementation for threshold ECDSA by Abram et al. (SP 2022) while incorporating an additional correlation.
